---
title: "Activity 2"
author: "Anik Shikarpuri"
date: "2023-01-20"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Instructions

  - The assignment must be submitted via Canvas.  
  - (2 pts) You should submit a HTML output file called `yourname_act2.nb.html`. 

### 1. (2 pts) Setting working directory

I recommend that you use the following hierarchical structures (folder and file names can be different):
```
STAT184 - Activity1 - activity1.Rmd
                    - activity1.html
                    - image.png
                    
        - Activity2 - activity2.Rmd
                    - activity2.nb.html
                    
        - Homework1 - hw1.Rmd
                    - hw1.nb.html
```

Print your current working directory.

getwd()

### 2. (4 pts) Vectors
Let our small data set be the following:
```
2 5 4 10 8
```

a. Enter this data into a vector `y`.

```{r}
y <- c(2, 5, 4, 10, 8)
y
```


b. Find the square of each number.
```{r}
sqrt(y)

```


c. Subtract 6 from each number.
```{r}
y-6
```


d. Subtract 9 from each number and then square the answers. 
```{r}
x= y-9
z= sqrt(x)
z     #Gives NaN for negative numbers becase they can't have a sqrt
```



### 3. (4 pts) Using `Help` documentation
For this question, please use the help documentation by using `?function_name` or `help(function_name)`.

a. Create a vector `x` which contains consecutive numbers from 1 to 10.
```{r}
x <- c(1,2,3,4,5,6,7,8,9,10)
```


b. Calculate the cumulative sum of the numbers in `x`. 
- **Hint**: read the documentation on the `cumsum` function using `?cumsum` or `help(cumsum)`.

```{r}
cumsum(x)

```

c. Calculate the cumulative sum of the numbers in `x`, but in reverse order. 
```{r}
rev(x)
```

d. Create a vector `y` which contains 5 random numbers between 1 and 10, rounded to the nearest whole number. 
- **Hint**: read the documentation on `sample`.
```{r}
y <- round(sample(1:10, 5, replace = TRUE))
y

```


### 4. (3 pts) Comments
Please write down comments after `#` to explain each line. 
```{r}
x <- rep(c(1,2,3,4,5), times = 2) # create a vector by replicating c(1,2,3,4,5) twice
x[1]    #this give the number at index 1 which is =1 
x[length(x)]  #this gives the length of the original vertex
x[1:3] # gives values from 1-3
```

### 5. Reading

Please read Data Computing Ebook Ch1 before you come to next Friday (1/27) class.

Here is the link to [Ch1](https://dtkaplan.github.io/DataComputingEbook/chap-tidy-data.html#chap:tidy-data) or you can find the book on Canvas. 

